Kernel Methods and SVMs: A convex optimization point of view

### 2016-05-28 coproject/report_2.tex
UPD: Updated beginning of the report

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\newtheorem{theorem}{Theorem}

@@

\subsubsection{Feature Mapping}

@@

@@

From section \ref{meth}, we already understand that the learning algorithm will have to find the best weights in order to have the most accurate prediction. The idea of the learning algorithm is to take a subset of the pre-trained examples, test the predictions, change the weight, etc. This can easily be seen as an optimization problem.

\subsection{From infinite to finite - The kernel trick}
\section{Support vector machines: a special case}
\subsection{Generalities}
\subsection{Dual problem}
\subsection{A use case}
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xcolor}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

@@

\subsubsection{Feature Mapping}
\label{map}

@@

{\color{red} Je devrais peut etre definir ici les RKHS}

@@

From section \ref{meth}, we already understand that the learning algorithm will have to find the best weights in order to have the most accurate prediction. The idea of the learning algorithm is to take a subset of the pre-trained examples, test the predictions, change the weight, etc. This can easily be seen as an optimization problem.  
\\\\

{\color{red} Je suis un peu perdu sur cette partie... }

\subsection{From infinite to finite}

{\bf \color{red} KERNEL TRICK + REPRESENTER THEOREM}

We saw in the section \ref{map}, we can use a feature map to go from the input space $\mathcal{X}$ to a Hilbert space of a very high or infinite dimension $\mathcal{H}$. However, having the explicit representation of the mapping can be difficult and it is not convenient to work with it because of the high dimension of $\mathcal{H}$. Therefore, the idea is to work implicitly in the feature space $\mathcal{H}$. In order to do this, we must define the kernel trick.

\begin{definition} [The Kernel trick]
We take any algorithm to process finite-dimensional vectors. If we can express this algorithms only in terms of pairwise inner products. Then this algorithm can be applied to potentially infinite-dimensional vectors in the feature space of a positive definite kernel if we replace each inner product evaluation by a kernel evaluation.
\end{definition}

Intuitively, the idea is that we will compute $K(x,x') = \langle\phi(x),\phi(x')\rangle_{\mathcal{H}}$ without even knowing the function $\phi(x)$ because it is often really complex.
\\\\

\section{Support vector machines: a special case}
\subsection{Generalities}
\subsection{Dual problem}
\subsection{A use case}
\end{document}
